A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-25 Paper.tex
Revisions to particle filter

			\subsubsection{Particle filter}
				Particle filters takes a probabilistic approach to estimating the initial location of the beacons. As mentioned in \cite{Thrun2002a}, initially the entire space is represented by particles. Particles refer to collection of sample states. These particles are re-sampled based on importance weights every iteration. There are several re-sampling methods mentioned in \cite{Li2015}. Eventually the particle set converges to the accurate location of the beacons. Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.

@@

\subsection{Particle Filters}      %change the references
Particles filters are a category of monte carlo algorithms. they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because of its ability to solve the global localization (THIS IS A FIXED CITATION, PUT ACTUAL CITATION HERE)[2] and the kidnapped robot problem \cite{Engelson1992} which EKF ,in comparison, struggles with. At is core, EKF also has higher dimensional computation problems.
% It has also been at the core higher dimensional computational problems.  
%Description
Initially robot assumes global uncertainty through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=50mm,width=95mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

\end{figure}
Assuming at time t=0;we have N particles equally space in the environment that are drawn based on a uniform distribution $ p(x_oa)$.                                                                        re sampling methods depending on computational complexities. After some iterations only th   p
Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$. It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$. Eventually the particle filter converges to give us the true positioning of the robot.

As mentioned in \cite{Thrun2002a} particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment. 
EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}
As the number of particles increases the computational complexity of the filter too increases. In order to address this there were several new methods introduced that  exploit the independence among state variables. For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from \cite{Yuan2012}. It also solves the data association problem previously unsolved by EKF.

In \cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM. It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small. This approach is validated for both simulated and real data sets. This approach is preferred in indoor applications where there is a high probability of multi path signal propagation.

>>>>

			\subsubsection{Particle filter}
				Particle filters takes a probabilistic approach to estimating the initial location of the beacons as mentioned in \cite{Thrun2002a}. Here, a particle refers to a  possible hypothesis of position of the landmark.

				Initially the robot assumes global uncertainty through a set of particles that are distributed all over the map as shown in Fig 2.(a). Hence the position of the landmarks are uncertain. As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one as shown in Fig.2(b). There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the initial location of the landmarks as shown in Fig.2(c).
				\begin{figure}[h!]
					\centering
					\includegraphics[height=35mm,width=90mm]{Particle_filter_method.JPG}
					\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed. The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the landmark location. }

				\end{figure}
				Assuming at time t=0;we have N particles equally space in the environment that are drawn based on a uniform distribution $ p(x_oa)$.                                                                       
				Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$. It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$. Eventually the particle filter converges to give us the true positioning of the landmarks.
				 These particles are re-sampled based on importance weights every iteration. There are several re-sampling methods mentioned in \cite{Li2015}. Eventually the particle set converges to the accurate location of the beacons.

@@

\subsection{Particle Filters}      %change the references
Particles filters are a category of monte carlo algorithms. They are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because of its ability to solve the global localization \cite{Borenstein1996} and the kidnapped robot problem \cite{Engelson1992} which EKF, in comparison, struggles with. At is core, EKF also has higher dimensional computation problems.
% It has also been at the core higher dimensional computational problems.  
%Description
As mentioned in \cite{Thrun2002a} particle filters outperform EKF in applications involving global localization (the kidnapped robot problem) where the robot is randomly picked up and placed in a unknown environment. 
EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}.

It works in a similar way to the particle filter initialization procedure mentioned before, but it uses a weighted average of both the possible landmark and robot positions to converge to the actual robot and landmark locations.
As the number of particles increases the computational complexity of the filter too increases. In order to address this there were several new methods introduced that  exploit the independence among state variables. For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from \cite{Yuan2012}. It also solves the data association problem previously unsolved by EKF. Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.

   \cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM. It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small. This approach is validated for both simulated and real data sets. This approach is preferred in indoor applications where there is a high probability of multi path signal propagation.
